Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-17 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
修改拼写错误

Recently, some Siamese trackers~\cite{SiamRPN,SiamRPN++,SiamFC++} have demonstrated a significant performance improvement in visual tracking. 
In particular, SiamRPN \cite{SiamRPN} consists of one Siamese subnetwork for feature extraction and another region proposal subnetwork including the classification and regression branches separately. Based on its success in decomposition of classification and state estimation, SiamRPN++ \cite{SiamRPN++} further breaks the restriction of strict translation invariance through a simple yet effective spatial aware sampling strategy and successfully trains a ResNet-driven Siamese tracker with significant performance gains. Apart from these anchor-based methods, an anchor-free tracker SiamFC++ \cite{SiamFC++} is further designed by considering non-ambiguous scoring, prior target scale/ratio distribution knowledge-free and estimation quality assessment guidelines .
In our experiments, we are focused on the anchor-free SiamFC++ tracker, whereas the transferability of our generated adversarial attacks to the previous anchor-based trackers is also studied.

@@

\textit{Imperceptible Perturbations v.s. Adversarial Patch.} The imperceptible perturbations most commonly modify each pixel by a small amount and can be found using a number of optimisation strategies such as Limited-memory BFGS \cite{intriguing} and PGD \cite{PGD}.
Different from the imperceptible perturbations, the adversarial patch is extremely salient to a neural network. The adversarial patch can be placed anywhere into the input image to cause the network to misbehave, and thus is commonly used for universal attacks \cite{patch}.
To the best of our knowledge, we are the first to attack object trackers utilizing both the imperceptible perturbations and adversarial patch together, which are jointly trained in an end-to-end manner.
Note that our adversarial patch works in the network domain instead of the image domain. In the network-domain case, the noise is allowed to take any value and is not restricted to the dynamic range of images as in the image-domain case \cite{karmon2018lavan}.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.93\textwidth]{images/vis_v3.pdf}
\caption{The results under targeted attacks. Red represents a ground-truth bounding box, yellow represents the specific bounding box, and green represents the predicted bounding box by trackers. The yellow and green boxes are basically the same in time series, which indicates that targeted attack is successful.}
\label{fig:vis}
\end{figure*}

@@

GOT-10k \cite{GOT-10k} is a recent large-scale high-diversity dataset. There is no overlap in object classes between the train/val/test splits, promoting the importance of generalization to unseen object classes.
%Because we need to use the real ground truth to generate the fake ground truth, and the fake ground truth is not available on test set, so we use the val set.
%The evaluation metric is AO and Success rate, which means ...
We use average overlap (AO) for evaluation.
The AO relative to $B^{fake}$ on the adversarial videos is 0.818, which demonstrates that the generated universal perturbations can mislead the track to follow a specified trajectory (see Figure \ref{fig:vis}).
%On GOT-10k Val set, the AO relative to $B^{gt}$ on the clean videos is 0.760. The AO relative to $B^{gt}$ on the adversarial videos is 0.023.

>>>>

Recently, some Siamese trackers~\cite{SiamRPN,SiamRPN++,SiamFC++} have demonstrated a significant performance improvement in visual tracking. 
In particular, SiamRPN \cite{SiamRPN} consists of one Siamese subnetwork for feature extraction and another region proposal subnetwork including the classification and regression branches separately. Based on its success in the decomposition of classification and state estimation, SiamRPN++ \cite{SiamRPN++} further breaks the restriction of strict translation invariance through a simple yet effective spatial aware sampling strategy and successfully trains a ResNet-driven Siamese tracker with significant performance gains. Apart from these anchor-based methods, an anchor-free tracker SiamFC++ \cite{SiamFC++} is further designed by considering non-ambiguous scoring, prior target scale/ratio distribution knowledge-free and estimation quality assessment guidelines.
In our experiments, we are focused on the anchor-free SiamFC++ tracker, whereas the transferability of our generated adversarial attacks to the previous anchor-based trackers is also studied.

@@

\textit{Imperceptible Perturbations v.s. Adversarial Patch.} The imperceptible perturbations most commonly modify each pixel by a small amount and can be found using a number of optimisation strategies such as Limited-memory BFGS \cite{intriguing} and PGD \cite{PGD}.
Different from the imperceptible perturbations, the adversarial patch is extremely salient to a neural network. The adversarial patch can be placed anywhere into the input image to cause the network to misbehave, and thus is commonly used for universal attacks \cite{patch}.
To the best of our knowledge, we are the first to attack object trackers utilizing both the imperceptible perturbation and the adversarial patch together, which are jointly trained in an end-to-end manner.
Note that our adversarial patch works in the network domain instead of the image domain. In the network-domain case, the noise is allowed to take any value and is not restricted to the dynamic range of images as in the image-domain case \cite{karmon2018lavan}.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.93\textwidth]{images/vis_v3.pdf}
\caption{The results under targeted attacks. Red represents a ground-truth bounding box, yellow represents the specific bounding box, and green represents the predicted bounding box by trackers. The yellow and green boxes are basically the same in time series, which indicates that the targeted attack is successful.}
\label{fig:vis}
\end{figure*}

@@

GOT-10k \cite{GOT-10k} is a recent large-scale high-diversity dataset. There is no overlap in object classes between the train/val/test splits, promoting the importance of generalization to unseen object classes.
%Because we need to use the real ground truth to generate the fake ground truth, and the fake ground truth is not available on test set, so we use the val set.
%The evaluation metric is AO and Success rate, which means ...
We use the average overlap (AO) for evaluation.
The AO relative to $B^{fake}$ on the adversarial videos is 0.818, which demonstrates that the generated universal perturbations can mislead the track to follow a specified trajectory (see Figure \ref{fig:vis}).
%On GOT-10k Val set, the AO relative to $B^{gt}$ on the clean videos is 0.760. The AO relative to $B^{gt}$ on the adversarial videos is 0.023.
